\bf Nonparametric Block Bootstrap Kolmogorov-Smirnov Goodness-of-Fit Test

### 2025-05-22 manuscript/manuscript.tex
blk2004 results

We now consider the case where $X_i$'s are realizations from a time series and
$X^{(b)}_1,...,X^{(b)}_n$ are generated by block bootstrap for 
$b \in \{1, \ldots, B\}$.  
Circular block-bootstrap can be done with overlapping blocks that can
wrap around the end of the series \citet{romano1992circular}.
Define blocks (assuming block size $l > 1$) as:
\begin{equation*}
Z_j =
    \begin{cases}
        \{X_j, \ldots, X_{j + l - 1}\}, & j = 1, \dots, n - l + 1,\\
        \{X_j, \ldots, X_n, X_1, \ldots, X_{j-n+l-1}\}, & j = n - l
        + 2 ,\dots, n.
    \end{cases}
\end{equation*}
A common 
function for block size that is considered optimal is 
$l = \lceil n^{1/3} \rceil$ \citep{buhlmann1999block},  
which was adopted in this study. \citet{hall1995blocking} and 
\citet{politis2004automatic} note that
the selection of block size should ideally take into account the strength
and direction of serial dependence. However,
because this method is intended for cases where the dependence structure is 
unknown, the block size choice will not vary with the level of dependence.
Now we draw $k$ blocks from the $(n - l + 1)$ blocks 
of $Z_j$'s with replacement and then align them in the order they were picked to
form a block bootstrap sample. If $n$ is not a multiple of~$l$, the last block 
selected will be reduced in size so that the final size of the block bootstrap 
sample is $n$.

@@

>>>>

We now consider the case where $X_i$'s are realizations from a time series and
$X^{(b)}_1,...,X^{(b)}_n$ are generated by block bootstrap for
$b \in \{1, \ldots, B\}$.
Circular block-bootstrap can be done with overlapping blocks that can
wrap around the end of the series \citet{romano1992circular}.
Define blocks (assuming block size $l > 1$) as:
\begin{equation*}
Z_j =
    \begin{cases}
        \{X_j, \ldots, X_{j + l - 1}\}, & j = 1, \dots, n - l + 1,\\
        \{X_j, \ldots, X_n, X_1, \ldots, X_{j-n+l-1}\}, & j = n - l
        + 2 ,\dots, n.
    \end{cases}
\end{equation*}
A common
function for block size that is considered optimal is
$l = \lceil n^{1/3} \rceil$ \citep{buhlmann1999block}... \citet{hall1995blocking}
and
\citet{politis2004automatic} note that
the selection of block size should ideally take into account the strength
and direction of serial dependence. The plug-in approach for circular
bootstrap introduced in \citet{politis2004automatic}...
Now we draw $k$ blocks from the $(n - l + 1)$ blocks
of $Z_j$'s with replacement and then align them in the order they were picked to
form a block bootstrap sample. If $n$ is not a multiple of~$l$, the last block
selected will be reduced in size so that the final size of the block bootstrap
sample is $n$.

@@

\section{Appendix}\label{sec:appendix}
In our original setting, we used a block size of $l = \lceil n^{1/3} \rceil$.
However, the optimal block size may vary according to the dependence structure.
To address this, we considered  using the automatic block-length selection
scheme
for
circular block boostrap as described in Section 3.3 of
\citet{politis2004automatic}. Unfortunately, using this setting results in
the selection of
block
sizes that can be quite large (sometimes as large or larger than $n$), leading
to less variation between the bootstrapped
samples. Figures~\ref{fig:large_block_normal} and \ref{fig:large_block_gamma}
demonstrate that for highly temporally
dependent samples (especially when the autocorrelation is negative),
the block size is frequently larger than $\sqrt{n}$.

\begin{figure}[tbp]
  \centering
  \includegraphics[scale=1]{figures/large_block_normal}
  \caption{Proportion of selected block sizes using
  \citet{politis2004automatic}'s procedure that are larger than the sample size
    $n$ for $n \in \{100, 200, 400, 800\}$,
    $\tau \in \{-0.75, -0.5, -0.25, 0, 0.25, 0.5, 0.75\}$, and true marginal distribution
    $N(8,8)$.
  }
  \label{fig:large_block_normal}
\end{figure}

\begin{figure}[tbp]
  \centering
  \includegraphics[scale=1]{figures/large_block_gamma}
  \caption{Proportion of selected block sizes using
  \citet{politis2004automatic}'s procedure that are larger than the sample size
    $n$ for $n \in \{100, 200, 400, 800\}$,
    $\tau \in \{-0.75, -0.5, -0.25, 0, 0.25, 0.5, 0.75\}$, and true marginal distribution
    $\Gamma(8,1)$.
  }
  \label{fig:large_block_gamma}
\end{figure}

### 2025-05-22 manuscript/reply.tex
blk2004 results

The manuscript has been
revised accordingly with the following notable changes:
\begin{enumerate}
\item 
\item 
\item 
\item 
\end{enumerate}

@@

Thank you for your comment and the suggested literature. The primary 
methodological 
advancement in this study is a new bias correction - which is different than 
that introduced by \citet{babu2004goodness} - for cases where the dependence
structure of the data is not known. Therefore, in practical application,
the level of dependence may not be available to inform our choice of block
size. We have added a discussion of this limitation in the first paragraph of 
the NPBB for stationary
series subsection.

@@

Thank you. This is an interesting direction to investigate. We have added a few
sentences concerning potential future investigation into evaluating a bias 
correction for these variants in the second paragraph of the Discussion 
section.

>>>>

The manuscript has been
revised accordingly with the following notable changes:
\begin{enumerate}
\item An appendix outlining trial and issues with automatic block size selection
for circular block bootstrap.
\item Stronger justification of the bias term

\end{enumerate}

@@

Thank you for your comment and the suggested literature. We 
tried selecting block sizes using the plug-in approach 
from \citet{politis2004automatic}, which is outlined in the Appendix. 
Unfortunately, the procedure can result
in quite large block sizes that would result in the failure of the block
bootstrap step.

@@

Thank you. Our investigation actually used circular block bootstrap which
is a variant of moving block bootstrap, and we have appropriately changed
the terminology. Performance of other variants of 
bootstrap in our setting is an interesting direction to explore. We have added a 
few
sentences concerning potential future investigation into evaluating a bias 
correction for these variants in the second paragraph of the Discussion 
section.
